Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-16 Report/article.tex
figuref10

We notice the same complexity for both \texttt{Bit Majority} and \texttt{sum of integers}\autoref{fig:image_sf1}.
\begin{figure}[!H]%on ouvre l'environnement figure
\centering
\includegraphics[width=6cm, height=5cm]{f8.pdf} 
\caption{Wall time for sum} 
\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
\end{figure}

>>>>

We notice the same complexity for both \texttt{Bit Majority}\autoref{fig:image_sf0bis} and \texttt{sum of integers}\autoref{fig:image_sf1}.

\begin{figure}[!H]%on ouvre l'environnement figure
\centering
\includegraphics[width=6cm, height=5cm]{f8.pdf} 
\caption{Wall time for bit majority} 
\label{fig:image_sf0bis} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!H]%on ouvre l'environnement figure
\centering
\includegraphics[width=6cm, height=5cm]{f8.pdf} 
\caption{Wall time for sum} 
\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
\end{figure}
